---
title: "Import Data from the Cochrane Database of Systematic Reviews (CDSR)"
author: "Simon Schwab"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Import Data from the Cochrane Database of Systematic Reviews (CDSR)}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
The Cochrane Library is probably the largest body of evidence in health care. This packages loads data sets from systematic reviews from https://www.cochranelibrary.com that include all the study data, effect estimates, standard errors, sample sizes, the combined effect estimates from meta-analyses, and much more.

In this tutorial you load data from the Cochrane systematic review with ID `CD000059` titled "Clozapine versus typical neuroleptic medication for schizophrenia". The DOI is https://doi.org/10.1002/14651858.CD000059.pub2. We will then perform a meta-analysis of the comparison number 1, outcome number 3, as an example.

## Loading libraries

First we load the required packages for this tutorial. Obviously this is the `cochrane` package to access the data. The package `meta` is also required to perform the meta-analysis.
```{r, message=FALSE}
library(cochrane)
library(meta)
```

## Loading the data

You only need the DOI of the review and a folder were the file is downloaded.
```{r}
mydoi = c("https://doi.org/10.1002/14651858.CD000059.pub2")
dl_path = "~/Downloads"

get.review(doi = mydoi, dl_path, show.terms = TRUE)
```

The other option to access the data is to go to the Website of that specific review (https://doi.org/10.1002/14651858.CD000059.pub2) and manually download the data file by clicking "Download Statistical Data" in the right box at the bottom. Once you have the data in your Download folder, the following command will load the data:
```{r}
review = read.review(file = "CD000059StatsDataOnly.rm5", path = dl_path)
```

## Working with the data

The `read.review()` function will return a list with two data frames: the first contains all the study data, the second all the meta-analyses.
```{r}
studies = review[[1]]
ma = review[[2]]
```

Let's select the meta-analysis we are interested in, comparison no. 1, outcome no. 3. The outcome was dichotomous (`DICH`), that is the number of patients "not clinical improved" (see outcome `name`). The combined effect estimate (here, risk ratio) is 0.76 (95%-CI from 0.71 to 0.81). This means the treatment group (Clozapine) had a 0.76-fold risk (aka a 24% reduction of risk) for no clinical improvement (compared to the control group).
```{r}
tab.ma = ma[ma$outcome.id == "CMP-001.03",]
tab.ma
```

Next, you can select the studies that belong to this meta-analysis (i.e., comparison 1, outcome 3). There were 17 study results in the meta-analyses. The outcome of the studies are seen in the variables `events1` and `events2` for the intervention and control arm, respectively. The first group is always the intervention arm by convention.

```{r}
idx = studies$comparison.nr == 1 & studies$outcome.nr == 3
tab.studies = studies[idx,]
tab.studies
```
Now, we can perform the meta-analysis and see if we get the same result as reported above. We use the `meta` package for this. For the fixed-effect model we get the exact same estimate (and 95%-CI). So the systematic reviewers performed a fixed-effect analysis here.

```{r}
myma = metabin(event.e = events1, n.e = total1,
               event.c = events2, n.c = total2,
               RR.Cochrane = TRUE, Q.Cochrane = TRUE, sm = "RR", data = tab.studies)
summary(myma)
```

